Protecting Private Data in the Cloud: A Path Oblivious RAM Protocol

### 2014-11-18 paper/paper.tex
changed citations, updated bibliography

Previous works have shown the importance in protecting access pattern. Memory access patterns can leak information such as a program’s control flow, which concerns conditional branches of the program and the order of commands executed \cite{Zhuang}. Also, M.S. Islam et al. have shown how, from an encrypted email repository, adversaries can infer 80\% of search queries simply from access patterns \cite{Islam}.

@@

In the past three decades, researchers have strived to improve the efficiency and reduce the trusted storage requirement of ORAM \cite{Goldreich, Goodrich, Ostrovsky, Shi, Stefanov1}. A breakthrough in implementation is achieved through Path ORAM \cite{Stefanov2}. Path ORAM’s performance and trusted storage requirement are both logarithmic in its capacity. Furthermore, its algorithm is extremely simple and suitable for real world implementation. Immediately after its proposal in 2012, Path ORAM gained popularity in many applications due to its simplicity and efficiency. In this work, we adapted it for use with Dropbox.

@@

We summarize how Path ORAM works here. The reader can refer to \cite{Stefanov2} for more details. The tree is a binary tree data structure of height $L$ and $2^L$ leaves stored on the server as a one-dimensional array. The levels are numbered 0 to $L$, where level 0 is the root, level $L$ contains the leaves (in a complete tree), and levels in between contain non-leaf nodes. Each node in the binary tree is called a bucket, and contains $z$ blocks. If a bucket contains less than $z$ “real” blocks, the remainder are composed of dummy blocks, which are indistinguishable from real blocks because buckets are stored as encrypted fixed-size arrays.

@@

The first problem we encounter is to determine when to resize. Previous work suggested that the optimal utilization (meaning the fraction data block slots that are used) is around 50\% \cite{Ren}.

@@

For all the experiments except the one in Section 5.5, we utilize a distribution of files of various sizes to better simulate the contents/actions of a “real” file system, by reading/writing 1000 files based upon this cumulative distribution. This file distribution was chosen from previous work done on file system workloads \cite{Roselli}, and is reproduced below in Figure 5-1.

@@

As noted in Section 4.1, we utilized multi-block fetching with segment grouping to improve the efficiency of our tree architecture. From the graph we can see that the optimal grouping size appears to be 3, which also indicates that multiple block fetching does improve performance. However, larger grouping sizes create more congestion in some paths. To compensate for congestion, a technique called background eviction has to be employed, which takes additional overhead \cite{Ren, Yu}.

>>>>

Previous works have shown the importance in protecting access pattern. Memory access patterns can leak information such as a program’s control flow, which concerns conditional branches of the program and the order of commands executed \cite{HIDE}. Also, M.S. Islam et al. have shown how, from an encrypted email repository, adversaries can infer 80\% of search queries simply from access patterns \cite{Islam12}.

@@

In the past three decades, researchers have strived to improve the efficiency and reduce the trusted storage requirement of ORAM \cite{G87, GM11, O90, SCSL11, SSS12}. A breakthrough in implementation is achieved through Path ORAM \cite{PathORAM}. Path ORAM’s performance and trusted storage requirement are both logarithmic in its capacity. Furthermore, its algorithm is extremely simple and suitable for real world implementation. Immediately after its proposal in 2012, Path ORAM gained popularity in many applications due to its simplicity and efficiency. In this work, we adapted it for use with Dropbox.

@@

We summarize how Path ORAM works here. The reader can refer to \cite{PathORAM} for more details. The tree is a binary tree data structure of height $L$ and $2^L$ leaves stored on the server as a one-dimensional array. The levels are numbered 0 to $L$, where level 0 is the root, level $L$ contains the leaves (in a complete tree), and levels in between contain non-leaf nodes. Each node in the binary tree is called a bucket, and contains $z$ blocks. If a bucket contains less than $z$ “real” blocks, the remainder are composed of dummy blocks, which are indistinguishable from real blocks because buckets are stored as encrypted fixed-size arrays.

@@

The first problem we encounter is to determine when to resize. Previous work suggested that the optimal utilization (meaning the fraction data block slots that are used) is around 50\% \cite{oram-isca13}.

@@

For all the experiments except the one in Section 5.5, we utilize a distribution of files of various sizes to better simulate the contents/actions of a “real” file system, by reading/writing 1000 files based upon this cumulative distribution. This file distribution was chosen from previous work done on file system workloads \cite{roselli2000comparison}, and is reproduced below in Figure 5-1.

@@

As noted in Section 4.1, we utilized multi-block fetching with segment grouping to improve the efficiency of our tree architecture. From the graph we can see that the optimal grouping size appears to be 3, which also indicates that multiple block fetching does improve performance. However, larger grouping sizes create more congestion in some paths. To compensate for congestion, a technique called background eviction has to be employed, which takes additional overhead \cite{oram-isca13, Yu14DSB}.
